---
title: "Non-model analysis"
author: "Suparna Chaudhry and Andrew Heiss"
date: "`r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r load-libraries, message=FALSE}
knitr::opts_chunk$set(fig.retina = 2,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 120))  # For output

library(tidyverse)
library(stringr)
library(forcats)
library(scales)
library(patchwork)
library(here)

source(here("lib", "graphics.R"))
source(here("lib", "pandoc.R"))
source(here("lib", "bayes.R"))

my.seed <- 1234
set.seed(my.seed)
```

```{r load-data, cache=TRUE, message=FALSE}
df.donor.country <- readRDS(here("Data", "data_clean", "df_donor_country.rds"))
df.donor <- readRDS(here("Data", "data_clean", "df_donor.rds"))
df.donor.us <- readRDS(here("Data", "data_clean", "df_donor_usaid.rds"))
df.country <- readRDS(here("Data", "data_clean",  "df_country.rds"))
df.country.aid <- readRDS(here("Data", "data_clean", "df_country_aid_no_imputation.rds"))

dcjw.questions.clean <- read_csv(here("Data", "data_clean", "dcjw_questions.csv"))
dcjw.responses.clean <- read_csv(here("Data", "data_clean", "dcjw_responses.csv"))
```

## Overall data summary

```{r data-summary}
num.countries <- df.country.aid %>% distinct(cowcode) %>% nrow()
num.years <- df.country.aid %>% distinct(year) %>% nrow()
year.first <- df.country.aid %>% distinct(year) %>% min()
year.last <- df.country.aid %>% distinct(year) %>% max()
```

Our data includes information about `r num.countries` countries across `r num.years` years (from `r year.first`–`r year.last`)


## Summary of variables in model

The values here are slightly different from what we had at ISA and MPSA (and our ISQ submission) because we're now using V-Dem 8.0 and AidData 3.1. 

```{r summary-vars-model, results="asis", message=FALSE}
coef.names <- read_csv(here("Data", "data_clean", "coef_names.csv"))

vars.to.summarize <- coef.names %>%
  filter(summarize == TRUE)

vars.summarized <- df.country.aid %>%
  select(one_of(vars.to.summarize$term)) %>%
  mutate(trade.pct.gdp = trade.pct.gdp / 100,  # This is scaled up for modeling
         total.oda = total.oda / 1000000) %>%
  gather(term, value) %>%
  filter(!is.na(value)) %>% 
  group_by(term) %>%
  summarize(N = n(),
            Mean = mean(value),
            Median = median(value),
            `Std. Dev.` = sd(value),
            Min = min(value),
            Max = max(value)) %>% 
  left_join(vars.to.summarize, by = "term") %>%
  arrange(summary_order) %>%
  select(Variable = term_clean_table, Source = source, 
         Mean, `Std. Dev.`, Median, Min, Max, N) %>%
  as.data.frame()

caption <- "Summary of all variables included in models {#tbl:var-summary}"
var.summary <- pandoc.table.return(vars.summarized, keep.line.breaks = TRUE, 
                                   round = 2, big.mark = ",",
                                   justify = "llcccccc", caption = caption, style = "multiline")

cat(var.summary)
cat(var.summary, file = here("Output", "tbl-var-summary.md"))
```


## Aid stuff

### Overall OECD aid

```{r summarize-oecd-aid}
df.country.aid %>%
  summarise(total = dollar(sum(total.oda))) %>% 
  pull(total) -> total.oecd.aid
```

OECD members donated `r total.oecd.aid` between 1981 and 2013.

```{r plot-oecd-aid}
plot.aid <- df.country.aid %>%
  group_by(year) %>%
  summarise(total = sum(total.oda))

fig.oecd.aid <- ggplot(plot.aid, aes(x = year, y = (total / 1000000000))) + 
  geom_line() +
  labs(x = NULL, y = "Total ODA commitments\n(billions of USD)") +
  scale_y_continuous(labels = dollar) +
  theme_donors()
fig.oecd.aid
```

### Proportion of contentious vs. noncontentious aid

```{r summarize-contentious-aid, results="asis"}
df.donor %>%
  filter(year > 1980) %>%
  group_by(purpose.contentiousness) %>%
  summarise(total = sum(oda)) %>%
  mutate(perc = total / sum(total)) %>%
  mutate(total = dollar(total), perc = percent(perc)) %>% 
  pandoc.table()
```

```{r plot-contentious-aid}
plot.aid.contentiousness <- df.donor %>%
  filter(year > 1980) %>%
  group_by(year, purpose.contentiousness) %>%
  summarise(total = sum(oda)) %>%
  mutate(perc = total / sum(total)) %>%
  filter(purpose.contentiousness == "High")

fig.oecd.contention <- ggplot(plot.aid.contentiousness, aes(x = year, y = perc)) + 
  geom_line() +
  scale_y_continuous(labels = percent) + 
  labs(x = NULL, y = "Percent of\ncontentious aid") +
  theme_donors()
fig.oecd.contention
```

### USAID aid

```{r summarize-us-aid}
df.country.aid %>%
  summarise(total = dollar(sum(oda.us))) %>% 
  pull(total) -> total.us.aid

df.country.aid %>%
  filter(year > 1999) %>%
  summarise(total = dollar(sum(oda.us))) %>% 
  pull(total) -> total.us.aid.post.2000
```

The US donated `r total.us.aid` between 1981 and 2013 and `r total.us.aid.post.2000` between 2000 and 2013.

```{r plot-us-aid}
plot.aid.us <- df.country.aid %>%
  group_by(year) %>%
  summarise(total = sum(oda.us))

fig.us.aid <- ggplot(plot.aid.us, aes(x = year, y = (total / 1000000000))) + 
  geom_line() +
  labs(x = NULL, y = "Total US ODA commitments\n(billions of USD)") +
  scale_y_continuous(labels = dollar) +
  theme_donors()
fig.us.aid
```

### Proportion of US aid to types of NGOs

Total amounts over time:

```{r summarize-aid-channels, results="asis"}
usaid.total <- df.country.aid %>% summarise(total = sum(oda.us)) %>% as.numeric()

df.country.aid %>%
  gather(channel, total.oda.us, c(oda.us.ngo.dom, oda.us.ngo.int, oda.us.ngo.us)) %>%
  group_by(channel) %>%
  summarise(total = sum(total.oda.us)) %>%
  mutate(perc = total / usaid.total) %>%
  mutate(total = dollar(total), perc = percent(perc)) %>% 
  pandoc.table()
```

The US clearly favors US-based NGOs or international NGOs over domestic NGOs.

```{r plot-aid-channels}
usaid.total.yearly <- df.country.aid %>%
  group_by(year) %>%
  summarise(annual.total = sum(oda.us))

channels.nice <- tribble(
  ~channel,         ~channel.clean,
  "oda.us.ngo.dom", "Domestic NGOs",
  "oda.us.ngo.int", "International NGOs",
  "oda.us.ngo.us",  "US-based NGOs"
)

plot.usaid.channel <- df.country.aid %>%
  gather(channel, total.oda.us, c(oda.us.ngo.dom, oda.us.ngo.int, oda.us.ngo.us)) %>%
  group_by(year, channel) %>%
  summarise(total = sum(total.oda.us)) %>%
  left_join(usaid.total.yearly, by = "year") %>%
  mutate(perc = total / annual.total) %>%
  left_join(channels.nice, by = "channel")

fig.usaid.channel <- ggplot(plot.usaid.channel, 
                            aes(x = year, y = perc, colour = channel.clean)) + 
  geom_line() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + 
  scale_colour_manual(values = channel.colors) +
  labs(x = NULL, y = "Percent of US aid\ngiven through NGOs") +
  guides(colour = guide_legend(title = NULL, reverse = TRUE, nrow = 2)) +
  theme_donors()
fig.usaid.channel
```

USAID data categorizes all aid as government-channeled before 2000 because of some quirk in the data.

```{r plot-all-channels}
plot.usaid.channels.all <- df.donor.us %>%
  group_by(year, channel_subcategory_name) %>%
  summarise(total = sum(oda.us.2011)) %>%
  mutate(perc = total / sum(total)) %>%
  mutate(channel = ifelse(str_detect(channel_subcategory_name, "NGO"), "NGO", "Other"))

ggplot(plot.usaid.channels.all, 
       aes(x = year, y = perc, colour = channel_subcategory_name)) + 
  geom_line() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + 
  labs(x = NULL, y = "Percent of US aid given through different channels") +
  guides(colour = guide_legend(title = NULL)) +
  theme_donors()
```

So we just look at aid after 2000.

```{r plot-channels-post-2000}
fig.usaid.channel.trimmed <- fig.usaid.channel +
  coord_cartesian(xlim = c(2000, 2013))
fig.usaid.channel.trimmed
```


### All DV figures combined (for paper)

```{r plot-all-dvs, fig.width=6, fig.height=3.75}
fig.dvs <- (fig.oecd.aid + fig.oecd.contention + 
              fig.us.aid + fig.usaid.channel.trimmed) + 
  plot_layout(nrow = 2)

fig.dvs
fig.save.cairo(fig.dvs, filename = "fig-dvs", width = 6, height = 3.75)
```


## Legal restrictions on NGOs

### Compulsory vs. burdensome registration

Laws requiring NGO registration aren't necessarily a sign of oppression—even the US requires that nonprofits that earn above a certain threshold register as 501(c)(3) organizations. Though the figure below shows that compulsory regulation have increased over time, actual restriction has occurred too. Burdensome registration is not just another standard layer of bureaucracy.

```{r compulsory-vs-burdensome, fig.width=4.5, fig.height=2.5}
autocracies <- df.country %>%
  group_by(cowcode) %>%
  summarise(polity.avg = mean(polity, na.rm = TRUE)) %>%
  mutate(autocracy = polity.avg < 7) %>%
  # These countries are missing polity scores
  mutate(autocracy = case_when(
    # Equatorial Guinea, Kuwait, Bahrain, UAE, Oman, Singapore
    .$cowcode %in% c(411, 690, 692, 696, 698, 830) ~ TRUE,
    # Serbia, Kosovo
    .$cowcode %in% c(340, 347) ~ FALSE,
    TRUE ~ .$autocracy
  ))

df.regulation <- df.country %>%
  left_join(autocracies, by = "cowcode") %>%
  group_by(year, autocracy) %>%
  summarise(`Registration required` = sum(ngo_register) / n(),
            `Registration burdensome` = sum(ngo_register_burden) / n()) %>%
  gather(type.of.law, value, -year, -autocracy) %>%
  mutate(autocracy = 
           factor(autocracy, levels = c(TRUE, FALSE),
                  labels = c("Autocracies", "Democracies")))

fig.regulation.burden <- ggplot(df.regulation, 
                                aes(x = year, y = value, colour = type.of.law)) +
  geom_line() + 
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0, 0.7)) +
  scale_colour_manual(values = burden.colors) +
  guides(colour = guide_legend(reverse = TRUE, title = NULL)) +
  labs(x = NULL, y = "Proportion of countries\nwith regulation") +
  theme_donors() +
  facet_wrap(~ autocracy)

fig.regulation.burden
fig.save.cairo(fig.regulation.burden, filename = "fig-regulation-burden",
               width = 4.5, height = 2.5)
```


### DCJW indexes

```{r dcjw-index-table, results="asis", message=FALSE}
dcjw.indexes <- read_csv(here("Data", "data_clean", "dcjw_index.csv")) %>%
  mutate(Laws = str_replace_all(Laws, "\n", "\n\n"))

caption <- "Description of indexes of NGO barriers {#tbl:ngo-barriers-index}"
dcjw.index.table <- pandoc.table.return(dcjw.indexes, keep.line.breaks = TRUE, 
                                        style = "grid", justify = "lll", caption = caption)

cat(dcjw.index.table)
cat(dcjw.index.table, file = here("Output", "tbl-ngo-barriers-index.md"))
```


### Number of countries with restrictive laws

```{r num-countries-laws, fig.width=11, fig.height=7, cache=TRUE}
df.ngo.restrictions.plot <- df.country %>%
  select(cowcode, year, const_assoc, political_parties, starts_with("ngo_")) %>%
  gather(restriction, value, -c(cowcode, year)) %>%
  group_by(year, restriction, value) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  left_join(dcjw.responses.clean, by = c("restriction", "value")) %>%
  mutate(restriction = factor(restriction,
                              levels = unique(dcjw.responses.clean$restriction),
                              ordered = TRUE))

plot.dcjw <- function(df) {
  df.levels <- dcjw.responses.clean %>%
    filter(restriction == df$restriction[[1]]) %>%
    left_join(dcjw.questions.clean, by = c("restriction" = "question_clean"))
  
  plot.title <- df.levels$question_display
  num.countries <- max(df.ngo.restrictions.plot$n)
  
  df.leveled <- df %>%
    mutate(value_clean = factor(value_clean, levels = df.levels$value_clean, 
                                ordered = TRUE))
  
  ggplot(df.leveled, aes(x = year, y = n, colour = value_clean)) + 
    geom_line() + 
    labs(x = NULL, y = NULL, title = plot.title) +
    coord_cartesian(ylim = c(0, num.countries)) +
    scale_y_continuous(sec.axis = sec_axis(~ . / num.countries,
                                           labels = percent_format(accuracy = 1))) +
    guides(colour = guide_legend(title = NULL)) +
    theme_donors(8)
}

plot.all.dcjw.raw <- df.ngo.restrictions.plot %>%
  split(.$restriction) %>%
  map(plot.dcjw)

plot.all.dcjw <- arrangeGrob(grobs = plot.all.dcjw.raw, ncol = 3)
grid::grid.draw(plot.all.dcjw)
```

### NGO restrictions by type

```{r ngo-laws-type}
df.restrictions.type <- df.country %>%
  select(year, advocacy, association, entry, funding) %>%
  gather(barrier, value, -year) %>%
  group_by(year, barrier) %>%
  nest() %>% 
  mutate(cis = data %>% map(~ mean_cl_normal(.$value))) %>% 
  unnest(cis) %>% 
  mutate(barrier = factor(barrier, 
                          levels = unique(dcjw.questions.clean$barrier),
                          labels = unique(dcjw.questions.clean$barrier_display),
                          ordered = TRUE))

fig.ngo.barriers <- ggplot(df.restrictions.type, aes(x = year, y = y, colour = barrier)) +
  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = barrier), alpha = 0.3, colour = NA) +
  geom_line(aes(linetype = barrier)) +
  labs(y = "Average number of barriers", x = NULL) +
  scale_colour_manual(values = barrier.colors) +
  scale_fill_manual(values = barrier.colors) +
  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) +
  guides(colour = guide_legend(title = NULL),
         fill = guide_legend(title = NULL),
         linetype = guide_legend(title = NULL)) +
  theme_donors()
fig.ngo.barriers
```

### CSRE over time

```{r plot-csre-time}
df.csre.plot <- df.country %>%
  select(year, csre) %>%
  group_by(year) %>%
  nest() %>% 
  mutate(cis = data %>% map(~ mean_cl_normal(.$csre))) %>% 
  unnest(cis)

fig.csre <- ggplot(df.csre.plot, aes(x = year, y = y)) +
  geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.2) +
  geom_line() +
  labs(y = "Average civil society\nregulatory environment", x = NULL) +
  theme_donors()
fig.csre
```

### NGO barriers combined (for paper)

```{r plot-all-ngo-barriers, fig.width=6}
fig.barriers <- (fig.ngo.barriers + fig.csre) + plot_layout(ncol = 2)

fig.barriers
fig.save.cairo(fig.barriers, filename = "fig-barriers",
               width = 6, height = 2.5)
```


## Aid

### Aid over time, by donor type

```{r aid-by-donor}
aid.donor.type.time <- df.donor.country %>%
  group_by(year, donor.type.collapsed) %>%
  summarise(total.aid = sum(oda, na.rm = TRUE))

ggplot(aid.donor.type.time, aes(x = year, y = total.aid / 1000000000,
                                colour = donor.type.collapsed)) +
  geom_line() +
  labs(x = NULL, y = "Billions of USD",
       caption = "Source: OECD and AidData. 2011 dollars.") +
  guides(colour = guide_legend(title = NULL)) +
  scale_y_continuous(labels = dollar) + 
  theme_donors()
```

### Aid over time, by contentiousness

```{r aid-by-contention}
aid.contention.time <- df.donor.country %>%
  group_by(year, purpose.contentiousness) %>%
  summarise(total.aid = sum(oda, na.rm = TRUE))

ggplot(aid.contention.time, aes(x = year, y = total.aid / 1000000000,
                                colour = purpose.contentiousness)) +
  geom_line() +
  labs(x = NULL, y = "Billions of USD",
       caption = "Source: OECD and AidData. 2011 dollars.") +
  guides(colour = guide_legend(title = NULL)) +
  scale_y_continuous(labels = dollar) + 
  theme_donors()
```
