---
title: "Non-model analysis"
author: "Suparna Chaudhry and Andrew Heiss"
date: "`r format(Sys.time(), '%F')`"
output: 
  html_document: 
    code_folding: hide
    css: ../html/fixes.css
    fig_height: 3.5
    fig_width: 5
    highlight: pygments
    includes:
      after_body: ../html/add_home_link.html
    theme: spacelab
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r load-libraries, message=FALSE}
knitr::opts_chunk$set(cache=FALSE, fig.retina=2,
                      tidy.opts=list(width.cutoff=120),  # For code
                      options(width=120))  # For output

library(tidyverse)
library(stringr)
library(forcats)
library(DT)

source(file.path(PROJHOME, "lib", "graphics.R"))
source(file.path(PROJHOME, "lib", "pandoc.R"))
source(file.path(PROJHOME, "lib", "bayes.R"))

my.seed <- 1234
set.seed(my.seed)
```

```{r load-data, cache=TRUE, message=FALSE}
df.donor.country <- readRDS(file.path(PROJHOME, "Data", "data_clean",
                                      "df_donor_country.rds"))
df.donor <- readRDS(file.path(PROJHOME, "Data", "data_clean",
                              "df_donor.rds"))
df.donor.us <- readRDS(file.path(PROJHOME, "Data", "data_clean",
                                 "df_donor_usaid.rds"))
df.country <- readRDS(file.path(PROJHOME, "Data", "data_clean",
                                "df_country.rds"))
df.country.aid <- readRDS(file.path(PROJHOME, "Data", "data_clean",
                                "df_country_aid_no_imputation.rds"))

dcjw.questions.clean <- read_csv(file.path(PROJHOME, "Data", "data_clean",
                                           "dcjw_questions.csv"))
dcjw.responses.clean <- read_csv(file.path(PROJHOME, "Data", "data_clean",
                                           "dcjw_responses.csv"))
```

## Data summary

```{r data-summary}
num.countries <- df.country.aid %>% distinct(cowcode) %>% nrow()
num.years <- df.country.aid %>% distinct(year) %>% nrow()
year.first <- df.country.aid %>% distinct(year) %>% min()
year.last <- df.country.aid %>% distinct(year) %>% max()
```

Our data includes information about `r num.countries` countries across `r num.years` years (from `r year.first`–`r year.last`)

## Aid stuff

### Overall OECD aid

```{r}
df.country.aid %>%
  summarise(total = scales::dollar(sum(total.oda)))
```

```{r}
plot.aid <- df.country.aid %>%
  group_by(year) %>%
  summarise(total = sum(total.oda))

fig.oecd.aid <- ggplot(plot.aid, aes(x=year, y=(total / 1000000000))) + 
  geom_line() +
  labs(x=NULL, y="Total ODA commitments\n(billions of USD)") +
  scale_y_continuous(labels=scales::dollar) +
  theme_donors()
fig.oecd.aid
```

### Proportion of contentious vs. noncontentious aid

```{r}
df.donor %>%
  filter(year > 1980) %>%
  group_by(purpose.contentiousness) %>%
  summarise(total = sum(oda)) %>%
  mutate(perc = total / sum(total)) %>%
  datatable() %>%
  formatCurrency("total", "$", digits=0) %>%
  formatPercentage("perc", 2)
```

```{r}
plot.aid.contentiousness <- df.donor %>%
  filter(year > 1980) %>%
  group_by(year, purpose.contentiousness) %>%
  summarise(total = sum(oda)) %>%
  mutate(perc = total / sum(total)) %>%
  filter(purpose.contentiousness == "High")

fig.oecd.contention <- ggplot(plot.aid.contentiousness, aes(x=year, y=perc)) + 
  geom_line() +
  scale_y_continuous(labels=scales::percent) + 
  labs(x=NULL, y="Percent of contentious aid") +
  theme_donors()
fig.oecd.contention
```

### USAID aid

```{r}
df.country.aid %>%
  summarise(total = scales::dollar(sum(oda.us)))
```

```{r}
plot.aid.us <- df.country.aid %>%
  group_by(year) %>%
  summarise(total = sum(oda.us))

fig.us.aid <- ggplot(plot.aid.us, aes(x=year, y=(total / 1000000000))) + 
  geom_line() +
  labs(x=NULL, y="Total US ODA commitments\n(billions of USD)") +
  scale_y_continuous(labels=scales::dollar) +
  theme_donors()
fig.us.aid
```

### Proportion of US aid to types of NGOs

Total amounts over time:

```{r}
usaid.total <- df.country.aid %>% summarise(total = sum(oda.us)) %>% as.numeric()

df.country.aid %>%
  gather(channel, total.oda.us, c(oda.us.ngo.dom, oda.us.ngo.int, oda.us.ngo.us)) %>%
  group_by(channel) %>%
  summarise(total = sum(total.oda.us)) %>%
  mutate(perc = total / usaid.total) %>%
  datatable() %>%
  formatCurrency("total", "$", digits=0) %>%
  formatPercentage("perc", 2)
```

The US clearly favors US-based NGOs or international NGOs over domestic NGOs.

```{r}
usaid.total.yearly <- df.country.aid %>%
  group_by(year) %>%
  summarise(annual.total = sum(oda.us))

channels.nice <- tribble(
  ~channel, ~channel.clean,
  "oda.us.ngo.dom", "Domestic NGOs",
  "oda.us.ngo.int", "International NGOs",
  "oda.us.ngo.us", "US-based NGOs"
)

plot.usaid.channel <- df.country.aid %>%
  gather(channel, total.oda.us, c(oda.us.ngo.dom, oda.us.ngo.int, oda.us.ngo.us)) %>%
  group_by(year, channel) %>%
  summarise(total = sum(total.oda.us)) %>%
  left_join(usaid.total.yearly, by="year") %>%
  mutate(perc = total / annual.total) %>%
  left_join(channels.nice, by="channel")

fig.usaid.channel <- ggplot(plot.usaid.channel, 
                            aes(x=year, y=perc, colour=channel.clean)) + 
  geom_line() +
  scale_y_continuous(labels=scales::percent) + 
  scale_colour_manual(values=channel.colors) +
  labs(x=NULL, y="Percent of US aid given through NGOs") +
  guides(colour=guide_legend(title=NULL, reverse=TRUE)) +
  theme_donors()
fig.usaid.channel
```

USAID data categorizes all aid as government-channeled before 2000 because of some quirk in the data.

```{r}
plot.usaid.channels.all <- df.donor.us %>%
  group_by(year, channel_subcategory_name) %>%
  summarise(total = sum(oda.us.2011)) %>%
  mutate(perc = total / sum(total)) %>%
  mutate(channel = ifelse(str_detect(channel_subcategory_name, "NGO"), "NGO", "Other"))

ggplot(plot.usaid.channels.all, 
       aes(x=year, y=perc, colour=channel_subcategory_name)) + 
  geom_line() +
  scale_y_continuous(labels=scales::percent) + 
  labs(x=NULL, y="Percent of US aid given through different channels") +
  guides(colour=guide_legend(title=NULL)) +
  theme_donors()
```

So we just look at aid after 2000.

```{r}
fig.usaid.channel.trimmed <- fig.usaid.channel +
  coord_cartesian(xlim=c(2000, 2013))
fig.usaid.channel.trimmed
```


### All DV figures combined (for paper)

```{r}
# Extract legend and put it in its own grob
# http://www.sthda.com/english/wiki/ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page-r-software-and-data-visualization#change-legend-position
fig.dvs <- arrangeGrob(fig.oecd.aid, fig.oecd.contention, 
                       fig.us.aid, fig.usaid.channel.trimmed + 
                         theme(legend.position="none"),
                       plot.blank, extract_legend(fig.usaid.channel.trimmed), 
                       ncol=2,
                       heights=c(1, 1, 0.2))

grid::grid.newpage()
grid::grid.draw(fig.dvs)

fig.save.cairo(fig.dvs, filename="fig-dvs",
               width=6, height=5)
```


## Legal restrictions on NGOs

### DCJW indexes

```{r dcjw-index-table, results="asis", message=FALSE}
dcjw.indexes <- read_csv(file.path(PROJHOME, "Data", 
                                   "data_clean", "dcjw_index.csv")) %>%
  mutate(Laws = str_replace_all(Laws, "\n", "\n\n"))

caption <- "Description of indexes of NGO barriers {#tbl:ngo-barriers-index}"
dcjw.index.table <- pandoc.table.return(dcjw.indexes, keep.line.breaks=TRUE, 
                                        style="grid", justify="lll", caption=caption)

cat(dcjw.index.table)
cat(dcjw.index.table, file=file.path(PROJHOME, "Output",
                                     "tbl-ngo-barriers-index.md"))
```


### Number of countries with restrictive laws

```{r num-countries-laws, fig.width=11, fig.height=7}
df.ngo.restrictions.plot <- df.country %>%
  select(cowcode, year, const_assoc, political_parties, starts_with("ngo_")) %>%
  gather(restriction, value, -c(cowcode, year)) %>%
  group_by(year, restriction, value) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  left_join(dcjw.responses.clean, by=c("restriction", "value")) %>%
  mutate(restriction = factor(restriction,
                              levels=unique(dcjw.responses.clean$restriction),
                              ordered=TRUE))

plot.dcjw <- function(df) {
  df.levels <- dcjw.responses.clean %>%
    filter(restriction == df$restriction[[1]]) %>%
    left_join(dcjw.questions.clean, by=c("restriction" = "question_clean"))
  
  plot.title <- df.levels$question_display
  num.countries <- max(df.ngo.restrictions.plot$n)
  
  df.leveled <- df %>%
    mutate(value_clean = factor(value_clean, levels=df.levels$value_clean, 
                                ordered=TRUE))

  ggplot(df.leveled, aes(x=year, y=n, colour=value_clean)) + 
    geom_line() + 
    labs(x=NULL, y=NULL, title=plot.title) +
    coord_cartesian(ylim=c(0, num.countries)) +
    scale_y_continuous(sec.axis = sec_axis(~ . / num.countries,
                                           labels=scales::percent)) +
    guides(colour=guide_legend(title=NULL)) +
    theme_donors(8)
}

plot.all.dcjw.raw <- df.ngo.restrictions.plot %>%
  split(.$restriction) %>%
  map(plot.dcjw)

plot.all.dcjw <- arrangeGrob(grobs=plot.all.dcjw.raw, ncol=3)
grid::grid.draw(plot.all.dcjw)
```

### NGO restrictions by type

```{r ngo-laws-type}
df.restrictions.type <- df.country %>%
  select(year, advocacy, association, entry, funding) %>%
  gather(barrier, value, -year) %>%
  group_by(year, barrier) %>%
  by_slice(~ mean_cl_normal(.x$value)) %>%
  unnest() %>%
  mutate(barrier = factor(barrier, 
                          levels=unique(dcjw.questions.clean$barrier),
                          labels=unique(dcjw.questions.clean$barrier_display),
                          ordered=TRUE))

fig.ngo.barriers <- ggplot(df.restrictions.type, aes(x=year, y=y, colour=barrier)) +
  geom_ribbon(aes(ymin=ymin, ymax=ymax, fill=barrier), alpha=0.3, colour=NA) +
  geom_line() +
  labs(y="Average number of barriers", x=NULL) +
  scale_colour_manual(values=barrier.colors) +
  scale_fill_manual(values=barrier.colors) +
  guides(colour=guide_legend(title=NULL),
         fill=guide_legend(title=NULL)) +
  theme_donors()
fig.ngo.barriers
```

### CSRE over time

```{r plot-csre-time}
df.csre.plot <- df.country %>%
  select(year, csre) %>%
  group_by(year) %>%
  by_slice(~ mean_cl_normal(.x$csre)) %>%
  unnest()

fig.csre <- ggplot(df.csre.plot, aes(x=year, y=y)) +
  geom_ribbon(aes(ymin=ymin, ymax=ymax), alpha=0.2) +
  geom_line() +
  labs(y="Average civil society regulatory environment", x=NULL) +
  theme_donors()
fig.csre
```

### NGO barriers combined (for paper)

```{r}
fig.barriers <- arrangeGrob(fig.ngo.barriers + theme(legend.position="none"), 
                            fig.csre, 
                            extract_legend(fig.ngo.barriers), plot.blank,  
                            ncol=2,
                            heights=c(2, 0.2))

grid::grid.newpage()
grid::grid.draw(fig.barriers)

fig.save.cairo(fig.barriers, filename="fig-barriers",
               width=6, height=3)
```


## Aid

### Aid over time, by donor type

```{r aid-by-donor}
aid.donor.type.time <- df.donor.country %>%
  group_by(year, donor.type.collapsed) %>%
  summarise(total.aid = sum(oda, na.rm=TRUE))

ggplot(aid.donor.type.time, aes(x=year, y=total.aid / 1000000000,
                                colour=donor.type.collapsed)) +
  geom_line() +
  labs(x=NULL, y="Billions of USD",
       caption="Source: OECD and AidData. 2011 dollars.") +
  guides(colour=guide_legend(title=NULL)) +
  scale_y_continuous(labels=scales::dollar) + 
  theme_donors()
```

### Aid over time, by contentiousness

```{r aid-by-contention}
aid.contention.time <- df.donor.country %>%
  group_by(year, purpose.contentiousness) %>%
  summarise(total.aid = sum(oda, na.rm=TRUE))

ggplot(aid.contention.time, aes(x=year, y=total.aid / 1000000000,
                                colour=purpose.contentiousness)) +
  geom_line() +
  labs(x=NULL, y="Billions of USD",
       caption="Source: OECD and AidData. 2011 dollars.") +
  guides(colour=guide_legend(title=NULL)) +
  scale_y_continuous(labels=scales::dollar) + 
  theme_donors()
```
